Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Working on Chapter 4 text

\chapter{Instrumented Gypsum Board Wall Experiments}
Purpose
\section{Experimental Arrangement}
A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.

>>>>

\chapter{Instrumented Gypsum Board Wall Experiments}
Purpose
\section{Experimental Arrangement}
This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.  A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.

The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.  The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~ref\{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.  A thermocouple installed in this manner shown in Figure~ref\
